%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSpecialSubheading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small#1} & \small #2 \\
      \textit{\small#3} & \small #4 \\
      \textit{\small#5} & \small #6 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small#1} & \small #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-3pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Yi(Jennifer) Jiang} \\ \vspace{1pt}
    \small (404) 216-0986 $|$ \href{mailto:yjiang607@gatech.edu}{\underline{yjiang607@gatech.edu}} $|$ 
    \href{https://www.linkedin.com/in/jenjiang5/}{\underline{linkedin.com/in/jenjiang5}} $|$
    \href{https://github.com/jen051}{\underline{github.com/jen051}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSpecialSubheading
      {Georgia Institute of Technology}{Atlanta, GA}
      {Bachelor of Science in Computer Science, Specialization in Intelligence/System Architecture}{Dec.2026 (Anticipated)}
      {Masters of Science in Computer Science, Specialization in Computer Perception/Robotics}{Dec.2027 (Anticipated)}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Head Teaching Assistant}{Aug. 2024 -- Present}
      {College of Computing, Georgia Institute of Technology}{Atlanta, GA}
      \resumeItemListStart
        \resumeItem{Head TA for 800+ students in Discrete Mathematics and Honors Discrete Mathematics.}
        \resumeItem{Provided guidance in weekly lectures and office hours; graded and provided feedback on assignments and exams.}
        \resumeItem{Collaborated with professors and 40+ fellow TAs and assisted in curriculum design and assessment coordination.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Undergraduate Research Assistant}{Jan. 2024 -- May. 2024}
      {EPIC Lab, Georgia Institute of Technology}{Atlanta, GA}
      \resumeItemListStart
        \resumeItem{Collaborated with fellow Researchers to design a set of Python and Matlab toolbox programs for experimental data processing and analysis.}
        \resumeItem{Assisted Graduate Team Leads directly in experiments, worked with motion capture to collect data to better understand the bio-mechanics of stroke patients.}
        \resumeItem{Analyzed scientific journal articles and initiated discussions with team members weekly.}
    \resumeItemListEnd

    \resumeSubheading
      {Research Intern}{Jul. 2022 -- Aug. 2022}
      {University of Alberta}{Edmonton, AB, Canada}
      \resumeItemListStart
        \resumeItem{Explored applications of Natural Language Processing in education with Professor Paul Lu.}
        \resumeItem{Developed an educational web game inspired by NYT's \emph{Wordle} using NLP and word embedding.}
        \resumeItem{Developed a Python script that uses the Gensim Word2Vec algorithm to process a corpus of text.}
      \resumeItemListEnd
    % \resumeSubheading
    %   {Programming Team Lead}{Sept. 2020 -- Jun. 2023}
    %   {FIRST Robotics Team 4627}{Calgary, AB, Canada}
    %   \resumeItemListStart
    %     \resumeItem{Programming lead of a team of $\sim$40 students, responsible for project management and guiding new members}
    %     \resumeItem{Worked with Time-of-Flight sensors and REV encoders, created PID loops that controlled the main functionalities of the robot during the 2023 season}
    %     \resumeItem{Developed a robot vision system using OpenMV, MicroPython, and JSON pipelines during the 2022 season}
    %     \resumeItem{Led the team to semifinals in the 2023 Canadian Pacific Regional and Las Vegas Regional}
    %   \resumeItemListEnd
    % \resumeSubheading
    %   {Co-Founder, VP Administration}{Apr. 2021 -- Jun. 2022}
    %   {Calgary Youth Programming Club}{Calgary, AB, Canada}
    %   \resumeItemListStart
    %     \resumeItem{Organized a virtual hackathon in Nov. 2021 with over 200 participants}
    %     \resumeItem{Acted as the primary point of contact for sponsors, club executives, and club members}
    %   \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Fight and Furious} $|$ \emph{Python, MediaPipe, OpenCV, React, FastAPI, Git}}{Sept. 2024}
          \resumeItemListStart
            \resumeItem{Won 2nd Best Overall Project in HackGT11, a 36-hour hackathon with 500+ participants hosted by Georgia Tech.}
            \resumeItem{Developed a web app that educates people about self defense techniques with React.}
            \resumeItem{Created the backend Python script that computes the accuracy of the user's motions compared to the instructor sample using the MediaPipe human pose estimation model, OpenCV, and numpy.}
            \resumeItem{Assisted with relaying backend live video analysis to the frontend webpage using FastAPI and Streamlit library.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Logical Circuit Generative Model} $|$ \emph{Python, Jupyter Notebook, GAN, CSS, Git}}{Feb. 2024}
          \resumeItemListStart
            \resumeItem{Winner of the Intel Developer Cloud Track at Hackalytics 2024, the largest data science hackathon in US with over 1100 participants and 200 completed projects}
            \resumeItem{Developed a Generative Adversarial Network deep learning model that generates viable digital logic circuits}
            \resumeItem{Created the training loops for the model and analyzed a dataset of over 50,000 existing digital logic circuits}
          \resumeItemListEnd
              \resumeProjectHeading
          {\textbf{Crib Protective Services} $|$ \emph{Python, Tensorflow, Librosa, OpenCV, Streamlit, Git}}{Feb. 2025}
          \resumeItemListStart
            \resumeItem{Cleaned a dataset of 600+ baby cry audios; used tensorflow to train a custom AI to predicts baby crying reasons.}
            \resumeItem{Used librosa and pyaudio to analyze input audio recording of baby cries.}
            \resumeItem{Used OpenCV to create a motion detection model that detects parents if there is significant infant movements.}
            \resumeItem{Used Streamlit and port forwarding to implement end-to-end integration.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Skills and Other}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, C/C++, JavaScript, HTML/CSS, React, Node.js, MATLAB} \\
     \textbf{Relevant Knowledge}{: SQL, Git, Android Studio, FastAPI, Pandas, Pytorch, Numpy, Unity, Intel Developer Cloud, OpenCV, NLP, PID Control, GAN} \\
     \textbf{Relevant Coursework}: Object Oriented Programming, Data Structures and Algorithms, Systems and Networks, Intro to AI, Objects and Design, Design and Analysis Algorithms, Linear Algebra, Discrete Maths}\\
     \textbf{Clubs and Societies}: Kappa Alpha Theta sorority, Women's Book Club Exec, Girls Who Code, VGDev, Krav Maga, GT Hapkido}
 \end{itemize}


%-------------------------------------------
\end{document}
